Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-16 Paper2015.tex
Using 11pt instead of 12pt.
working progress

% Paper 2015
\documentclass[12pt,journal]{IEEEtran}

@@

A detailed model of the ANITA geometry was implemented in Geant4.
This is illustrated in overview in Fig.~\ref{fig:ANITAoverview}
Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}; a summary only is given here.
The spallation target is a tungsten cylinder of diameter \SI{0}{\cm} and length \SI{0}{\cm}.
The target is cooled by water and surrounded by a stainless-steel cooling jacket.
The target assembly with its cooling jacket appears as a small blue rectangle in Fig.~\ref{fig:ANITAoverview}.
Lead shielding blocks in the target region are also modelled, and shown in red Fig.~\ref{fig:ANITAoverview}.
A large electromagnet surrounding the target is modelled and shown in Fig.~\ref{fig:ANITAoverview} in grey (iron) and yellow (copper).
An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).
For brevity in this summary we only present results for the standard collimator size (\SI{10.2}{\cm} diameter); in the final paper we will present results for cylindrical collimators in the range from \SIrange{3}{30}{\cm} diameter.

@@

Simulations were conducted using Geant4 version~TBD.
The TBD intranuclear cascade model was selected in accordance with the results of earlier work~\cite{Platt13}, in which it performed well in simulations of neutron spallation in the region from \SIrange{0}{0}{\MeV}.\todo{Enter neutron energy range}
In the simulation protons were incident axially at an energy of \SI{180}{\MeV}.
Resulting gamma and neutron fields were evaluated at several locations.
In this paper results are presented for three of these: The Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0}{\m} downstream of the target, and the CUP-TOF, \SI{0}{m} downstream of the target.\todo{Enter CUP \& CUP-TOF ranges}
The SUP, CUP and CUP-TOF positions are visible in blue in Fig.~\ref{fig:ANITAoverview}.
The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).

@@

\begin{figure}[t]
    \vspace{2in}
    \todo{Show density of neutrons above \SI{10}{\MeV} at SUP}
    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Standard User Position.}
    \label{fig:SUPDensity}
\end{figure}

\begin{figure}[t]
    \vspace{2in}
    \todo{Show SUP profile, compared to measurements}
    \caption{Neutron profile at the Standard User Position}
    \label{fig:SUPProfile}
\end{figure}

@@

\begin{figure}[t]
    \vspace{2in}
	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
    \vspace{2in}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:SUPSpectraComparison}
\end{figure}

@@

\begin{figure}[t]
    \vspace{2in}
    \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Close User Position.}
    \label{fig:CUPDensity}
\end{figure}

\begin{figure}[t]
    \vspace{2in}
    \todo{Show CUP profile, compared to measurements}
    \caption{Neutron profile at the Close User Position}
    \label{fig:CUPProfile}
\end{figure}

@@

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionSUP}
    }\\
    \subfloat[CUP]{
        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionCUP}
    }
    \caption{Gamma spatial distribution}
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

\begin{figure}
    \centering
    \vspace{2in}
    \hspace{\columnwidth}
    \caption{Calculated differential gamma spectra at CUP and SUP}
    \label{fig:DifferentialGammaSpectra}
\end{figure}

>>>>

% Paper 2015
\documentclass[11pt,a4paper]{IEEEtran}

@@

A detailed model of the ANITA geometry was implemented in Geant4.
This is illustrated in overview in Fig.~\ref{fig:ANITAoverview}
Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}; a summary only is given here.
The spallation target is a tungsten cylinder of diameter \SI{5}{\cm} and length \SI{2.4}{\cm}.
The target is cooled by water and surrounded by a stainless-steel cooling jacket.
The target assembly with its cooling jacket appears as a small blue rectangle in Fig.~\ref{fig:ANITAoverview}.
Lead shielding blocks in the target region are also modelled, and shown in red Fig.~\ref{fig:ANITAoverview}.
A large electromagnet surrounding the target is modelled and shown in Fig.~\ref{fig:ANITAoverview} in grey (iron) and yellow (copper).
An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).
For brevity in this summary we only present results for the standard collimator size (\SI{10.2}{\cm} diameter); in the final paper we will present results for cylindrical collimators in the range from \SIrange{3}{30}{\cm} diameter.

@@

Simulations were conducted using Geant4 version 10.0.
The binary intranuclear cascade model was selected in accordance with the results of earlier work~\cite{Platt13}, in which it performed well in simulations of neutron spallation in the region from \SIrange{0}{0}{\MeV}.\todo{Enter neutron energy range}
In the simulation protons were incident axially at an energy of \SI{180}{\MeV}.
Resulting gamma and neutron fields were evaluated at several locations.
In this paper results are presented for three of these: The Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.\todo{Enter CUP \& CUP-TOF ranges}
The SUP, CUP and CUP-TOF positions are visible in blue in Fig.~\ref{fig:ANITAoverview}.
The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).

@@

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{SUP10ColSpatialDistribution10MeVRADECS.png}
% \todo{Show density of neutrons above \SI{10}{\MeV} at SUP}
    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Standard User Position.}
    \label{fig:SUPDensity}
\end{figure}

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{SUP10beamproFoldingRADECS.png}
% \todo{Show SUP profile, compared to measurements}
    \caption{Neutron profile at the Standard User Position}
    \label{fig:SUPProfile}
\end{figure}

@@

\begin{figure}[t]
    \vspace{2in}
%	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{ANITAIntYieldRADECS.eps}\hspace{\columnwidth}}\\
    \vspace{2in}
%	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{ANITALetYieldnormalisedRADECS.eps}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:SUPSpectraComparison}
\end{figure}

@@

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{CUP10ColSpatialDistribution10MeV.png}
% \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Close User Position.}
    \label{fig:CUPDensity}
\end{figure}

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{CUPTOF10beamproRADECS.png}
% \todo{Show CUP profile, compared to measurements}
    \caption{Neutron profile at the Close User Position}
    \label{fig:CUPProfile}
\end{figure}

@@

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
%	SUP10ColSpatialDistributionAllG
        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionSUP}
    }\\
    \subfloat[CUP]{
%    CUP10ColSpatialDistributionAllG
        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionCUP}
    }
    \caption{Gamma spatial distribution}
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

\begin{figure}
    \centering
    \vspace{2in}
    \hspace{\columnwidth}
    \includegraphics[width=3in]{gDYieldcomparedRADECS.eps}
    \caption{Calculated differential gamma spectra at CUP and SUP}
    \label{fig:DifferentialGammaSpectra}
\end{figure}
